\documentclass[8pt]{paper}

\usepackage[margin=8mm]{geometry}

\begin{document}

\line(1,0){800}

\begin{flushright}
Bryan John Kline\\
(513) 465-3629\\
bryan\_kline@mail.tmcc.edu\\
github.com/BryanKline\\
\end{flushright}

\begin{flushleft}
\large{\bfseries{Education:}}\\
[2mm]

University of Nevada Reno \begin{small}
(UNR)
\end{small} \hspace{52.5mm}Truckee Meadows Community College \begin{small}(TMCC)\end{small}\\
Bachelor of Science, Computer Science and Engineering \hspace{12.5mm} Associate of Science, Mathematics\\
$08/2012$ - $05/2013$ and $01/2015$ - Present \hspace{39mm} $08/2009$ - $05/2012$\\
GPA: $4.0$ \hspace{97mm} GPA: $4.0$\\
[2mm]

\large{\bfseries{Relevant Course Work:}}\\
[2mm]

CS105 \hspace{6mm} - Introduction to computing (Dr. Michael Leverington)\\
CS135 \hspace{6mm} - Introduction to C/C\begin{small}++\end{small} (Dr. David Feil-Seifer)\\
CS202 \hspace{6mm} - Classes and data structures in C\begin{small}++\end{small} (Nancy LaTourrette)\\
CS219 \hspace{6mm} - Computer organization (Dr. Dwight Egbert)\\
CS302 \hspace{6mm} - Data structures and algorithms in C\begin{small}++\end{small} (Dr. Michael Leverington)\\
CS36 \hspace{8mm} - Mathematics of computer science (Dr. Yaakov Varol)\\
CPE201 \hspace{3mm} - Fundamentals of computer engineering (Dr. Murat Yuksel)\\
CISCO120 - Introduction to networking (Dr. Bill Doherty)\\
	
\begin{small}(Transcipts available upon request)\end{small}\\
[2mm]

\large{\bfseries{Work History:}}\\
[2mm]

ASUN Campus Escort \hspace{70mm} UNR School of Medicine, Dep. of Pathology\\
Shuttle Bus Driver (student employee) \hspace{41mm} Histopathology Technician (classified employee)\\
University of Nevada Reno \begin{small}(UNR)
\end{small} \hspace{49.5mm} University of Nevada Reno \begin{small}(UNR)\end{small}\\
05/2015 - Present \hspace{79mm} 02/2013 - 08/2014\\
Christopher Patridge (Coordinator) \hspace{46mm} Lynda McLellan (Program Officer)\\
(775) 784-6589 \hspace{84mm} (775) 784-7034\\

\begin{small}(Detailed work history available upon request)\end{small}\\
[2mm]

\large{\bfseries{Personal Projects:}}\\
[2mm]

Anti-Frogger (web-based game)\\
Final project for CS135, produced jointly with classmate (Dalton Navalta)\\
Javascript\\
[1mm]
Campus Escort Automated Call System (Windows application)\\
GUI application created for current employer to interface with automated phone system to reduce call volume\\
C\begin{small}++\end{small} in an integrated development environment (QT)\\
[2mm]

\large{\bfseries{Self-Guided Learning:}}\\
[2mm]

Udemy.com \hspace{90mm} Udacity.com\\
Cisco networking bootcamp \hspace{61mm} Android development microdegree program\\
01/2015 - Present \hspace{79mm} 01/2016 - Present\\
[1mm]

Lynda.com \hspace{91mm} QT\\
Java training tutorials \hspace{71mm} C\begin{small}++\end{small} based IDE\\
01/2016 - Present \hspace{79mm} 11/2015 - Present\\
[1mm]

LaTex\\
Text editor for scientists and engineers\\
01/2016 - Present\\

\end{flushleft}

\line(1,0){800}\\

\end{document}







