\documentclass[8pt]{paper}

\usepackage[margin=8mm]{geometry}

\begin{document}

\line(1,0){800}

\begin{flushright}
Bryan John Kline\\
(513) 465-3629\\
bkline@nevada.unr.edu\\
github.com/BryanKline\\
\end{flushright}

\begin{flushleft}
\large{\bfseries{Education:}}\\
[2mm]

University of Nevada Reno \begin{small}
(UNR)
\end{small}\\ 
Bachelor of Science, Computer Science and Engineering\\
$08/2012$ - $05/2013$ and $01/2015$ - Present\\
GPA: $3.97$\\
[2mm]

\large{\bfseries{Relevant Course Work:}}\\
[2mm]

CS105 \hspace{6mm} - Introduction to computing (Dr. Michael Leverington)\\
CS135 \hspace{6mm} - Introduction to C/C\begin{small}++\end{small} (Dr. David Feil-Seifer)\\
CS202 \hspace{6mm} - Object oriented programming in C\begin{small}++\end{small} (Nancy LaTourrette)\\
CS219 \hspace{6mm} - Computer organization (Dr. Dwight Egbert)\\
CS302 \hspace{6mm} - Data structures and algorithms in C\begin{small}++\end{small} (Dr. Michael Leverington)\\
CS326 \hspace{6mm} - Programming languages, concepts, and implementation (Dr. Mircea Nicolescu)\\
CS365 \hspace{6mm} - Mathematics of computer science (Dr. Yaakov Varol)\\	
CS446 \hspace{6mm} - Principles of operating systems (Suman Bhunia)\\	
CS454 \hspace{6mm} - Reliability and security of computing systems (Dr. Arslan Munir)\\
CS456 \hspace{6mm} - Automata and formal languages (Nancy LaTourrette)\\
CS477 \hspace{6mm} - Analysis of algorithms (Dr. Monica Nicolescu)\\
CS485 \hspace{6mm} - Computer vision (Dr. Mircea Nicolescu)\\
CPE201 \hspace{2.75mm} - Fundamentals of computer engineering (Dr. Murat Yuksel)\\
CPE301 \hspace{2.75mm} - Introduction to embedded systems (Dr. Dwight Egbert)\\
CISCO120 - Introduction to networking (Dr. Bill Doherty)\\
MATH485 - Graph theory and combinatorics (Dr. Thomas Quint)\\
	
\begin{small}(Transcipts available upon request)\end{small}\\
[2mm]

\large{\bfseries{Work History:}}\\
[2mm]

Computer Science and Engineering Department \hspace{24mm} ASUN Campus Escort\\
Teaching Assistant (CS135) \hspace{60.5mm} Shuttle Bus Driver (student employee)\\
University of Nevada Reno \begin{small}(UNR)
\end{small} \hspace{49.5mm} University of Nevada Reno \begin{small}(UNR)\end{small}\\
08/2016 - Present \hspace{78.5mm} 05/2015 - 09/2016\\
Dr. David Fiel-Seifer (CS135 Professor) \hspace{38.5mm} Christopher Patridge (Coordinator)\\
(775) 784-6469 \hspace{84mm} (775) 784-6589\\

\begin{small}(Detailed work history available upon request)\end{small}\\
[2mm]

\large{\bfseries{Projects:}}\\
[2mm]

TextTree\\
GUI application that stores and organizes data using a tree-based data structure\\
Java (Swing) and C\begin{small}++\end{small}\\
[2mm]

ASUN Campus Escort data management script\\
Small script created for previous employer to manage service user data\\
Python\\
[2mm]

Kinetic Mathematics\\
Android app development project for a math professor at UNR (in progress)\\
Android (XML and Java)\\
[2mm]


\end{flushleft}

\line(1,0){800}\\

\end{document}
